Alien species

### 2023-09-28 alien_species.Rmd
Highlight the focus on vascular plants #80
Use ANO and GRUK data sets #79

## Introduction {#intro-ali}
This indicator represent the the ecological on-site effect from  alien species. Whilst the introduction of alien species is best considered a pressure variable, the relative abundance of alien species on a given location is seen here as a manifestation of this negative anthropogenic impact, and is therefore a valid condition indicator.

@@

_NOTE: I'm not sure, but I wonder if the 2021 GRUK data was a pilot project and that most GRUK data, and all future GRUK data, will not be included in this data set._

>>>>

## Introduction {#intro-ali}
This indicator represent the the ecological on-site effect from  alien species. In practice, the indicator is restricted to alien vascular plants. Whilst the introduction of alien species is best considered a pressure variable, the relative abundance of alien species on a given location is seen here as a manifestation of this negative anthropogenic impact, and is therefore a valid condition indicator.

@@

See also [this GitHub issue](https://github.com/NINAnor/ecosystemCondition/issues/79).
